The \dealii Library, Version 9.7

### 2025-08-07 9.7/paper.tex
Fix minor typos

\item Improved support for transfering solution vectors during mesh refinement
  (Section~\ref{subsec:solutiontransfer})

@@

\subsubsection{ArborX, a performance-portable geometric search library}
ArborX~\cite{prokopenko2025} is a library for geometric search on CPUs and GPUS.
The new ArborX 2.X series is not backward compatible with the older 1.X series.
Consequently, this incompatibility required an extensive rewrite of our wrappers to
support ArborX 2.X. As part of the rewrite, the template parameters had to
be changed. When using the wrappers with ArborX 1.X, \texttt{ArborX::BVH}
and \texttt{ArborX::DistributedTree} are templated on both the dimension and
the number types. When using the wrappers with ArborX 2.X, these classes are
templated on the geometric objects used for the leaf nodes of the
\texttt{ArborX::BVH}.

>>>>

\item Improved support for transferring solution vectors during mesh refinement
  (Section~\ref{subsec:solutiontransfer})

@@

\subsubsection{ArborX, a performance-portable geometric search library}
ArborX~\cite{prokopenko2025} is a library for geometric search on CPUs and GPUs.
The new ArborX 2.X series is not backward compatible with the older 1.X series.
Consequently, this incompatibility required an extensive rewrite of our wrappers to
support ArborX 2.X. As part of the rewrite, the template parameters had to
be changed. When using the wrappers with ArborX 1.X, \texttt{ArborX::BVH}
and \texttt{ArborX::DistributedTree} are templated on both the dimension and
the number types. When using the wrappers with ArborX 2.X, these classes are
templated on the geometric objects used for the leaf nodes of the
\texttt{ArborX::BVH}.
